Brief notes on erosion

### 2016-08-21 docs/Notes.tex
Added to latex notes. Discussed motion of a reference point for theta-L.

\subsection{Center of mass motion}
Consider the body's center of mass
\begin{equation}
(x_{cm}, y_{cm}) = \frac{1}{A} \iint (x, y) \, dA
\end{equation}
I did a calculation to determine the motion of the center of mass, given the interface velocity. The result that I get is
\begin{equation}
\td{}{t} (x_{cm}, y_{cm})  = -\frac{1}{A} \int (x(s), y(s)) V_n(s) \, ds
\end{equation}
I believe the sign is correct for $\nhat$ the inward pointing normal, so that $V_n$ is positive if the body is shrinking.

@@

>>>>

\subsection{Motion of a reference point}

\subsubsection{The center of mass}
Consider the body's center of mass
\begin{equation}
(x_{cm}, y_{cm}) = \frac{1}{A} \iint (x, y) \, dA
\end{equation}
I did a calculation to determine the motion of the center of mass, given the interface velocity. The result that I get is
\begin{equation}
\td{}{t} (x_{cm}, y_{cm})  = -\frac{1}{A} \int (x(s), y(s)) V_n(s) \, ds
\end{equation}
I believe the sign is correct for $\nhat$ the inward pointing normal, so that $V_n$ is positive if the body is shrinking.

@@

\subsubsection{The surface-average coordinates}
I believe this will be even simpler. Consider the average of the surface coordinates
\begin{equation}
(x_a, y_a) = \int (x(\alpha), y(\alpha)) \, d\alpha
\end{equation}
I believe that this point moves according to
\begin{equation}
\td{}{t} (x_a, y_a) = \int V_n \, (n_x, n_y) \, d\alpha
\end{equation}
